---
title: "NetActivityData"
author: 
-   name: Carlos Ruiz Arenas
    affiliation: Centro de Investigación Biomédica en Red de Enfermedades Raras (CIBERER), Barcelona, Spain
    email: carlos.ruiza@upf.edu
date: "`r Sys.Date()`"
package: NetActivityData
output: 
    BiocStyle::html_document:
        toc_float: true
vignette: >
    %\VignetteIndexEntry{"NetActivityData"}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installation

You can install the current release version of NetActivityData with:

```{r, eval = FALSE}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("NetActivityData")
```

You can install the development version of NetActivity from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("yocra3/NetActivityData")
```

```{r}
library(NetActivityData)
```

# Introduction

This package contains pre-trained models for their use with `r Githubpkg("yocra3/NetActivity")`. The package currently contains two models based on GO Biological Processes and KEGG pathways. One model was trained using GTEx data (`gtex_gokegg`) and the other with TCGA data (`tcga_gokegg`). Each model contains two objects: the matrix weights and the gene set annotation. 

# GTEx model 

The GTEx model has the weights coded in `gtex_gokegg`, a matrix containing 1,518 gene sets and 8,758 genes (using ENSEMBL ids):

```{r}
data(gtex_gokegg)
gtex_gokegg[1:5, c(1:4, 554)]
```

The annotation is encoded in the `gtex_gokegg_annot` object, a data.frame containing the gene set full names and the genes' weights:

```{r}
data(gtex_gokegg_annot)
head(gtex_gokegg_annot)
```


# TCGA model 

The TCGA model has the weights coded in `tcga_gokegg`, a matrix containing 1,518 gene sets and 8,758 genes (using ENSEMBL ids):

```{r}
data(tcga_gokegg)
tcga_gokegg[1:5, c(1:4, 554)]
```

The annotation is encoded in the `tcga_gokegg_annot` object, a data.frame containing the gene set full names and the genes' weights:

```{r}
data(tcga_gokegg_annot)
head(tcga_gokegg_annot)
```

The columns `Weights` and `Weights_SYMBOL` are lists, where each element is a named vector:

```{r}
tcga_gokegg_annot$Weights[[1]]
tcga_gokegg_annot$Weights_SYMBOL[[1]]
```

```{r}
sessionInfo()
```

